ICT and Future Productivity: Evidence and Theory of a GPT

### 2018-11-10 Latex/MacroLunch_Nov2018/Slides_Nov2018.tex
presentation is finished
maybe you can have a look to it and then we can discuss sometime early
next week?

\documentclass{beamer}
\usepackage[english]{babel}
\usepackage[latin1]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{verbatim}
\usepackage{caption}
\usepackage{float}
%\usepackage{natbib}
\usepackage{csquotes}
\usepackage{sansmathaccent}
\usepackage{subfigure}
\usepackage{multicol}
\pdfmapfile{+sansmathaccent.map}
\usepackage{mathtools}
\def \ourFigPath {../../} 
\def \MainFigures{../Draft_Summer2018/MainFigures}
\def \ourTablePath {../../Tables/} 
\def\myFigWidth{2.0in}

@@

\title[ICT]{ICT and Future Productivity: Evidence and Theory of a GPT}

@@

@@

		\item Key prediction: BC fluctuations of a particular kind of investment (research \& development (R\&D) $\rightarrow$ adoption) lead total factor productivity (TFP)

@@

	Fernald et al. (2017): ``R\&D and adoption cannot be the whole story''.

@@

		\item [$\rightarrow$] A variable with at least the right timing is investment in information and communication technologies (ICT)

@@

    \item Draw on the conclusions of the ICT literature (references!) to build a structural model to interpret the results.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% HERE HERE HERE
% - complete ICT literature references 
% - implement roadmap
% - edit title

@@

	\item ICT and productivity 
		\begin{itemize}
		\item Oliner \& Stichel (2000), Stiroh(2002), 
		\end{itemize}

@@

%%%%%%% Slide %%%%%%
\begin{frame}
\frametitle{Roadmap}

EDIT THIS LATER
\begin{enumerate} 
	\item SVAR analysis: identifying an ICT shock

	\item A two-sector endogenous growth model

@@

	\begin{itemize}
	\item ICT value added is less than 5\% of GDP (BEA, April 2018)

@@

	\item Prediction of multisector models (GHK): sectoral productivity increase leads to sectoral output becoming cheaper

@@

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{Results II}

@@

@@

\item[$\rightarrow$] Alternative specification filters out news to recover an alternative ICT shock series

@@

%%%%%%% Slide %%%%%%
\begin{frame}
\frametitle{Roadmap}

EDIT THIS LATER
\begin{enumerate} 
	\item SVAR analysis: identifying an ICT shock

	\item A two-sector endogenous growth model

@@

	\begin{itemize}
	\item Belongs to the class of (GHK) models

	(we use isomorphic formulation of Oulton)

@@

>>>>

\documentclass{beamer}
\usepackage[english]{babel}
\usepackage[latin1]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{verbatim}
\usepackage{caption}
\usepackage{float}
%\usepackage{natbib}
\usepackage{csquotes}
\usepackage{sansmathaccent}
\usepackage{subfigure}
\usepackage{multicol}
\pdfmapfile{+sansmathaccent.map}
\usepackage{mathtools}
\def \ourFigPath {../../} 
\def \MainFigures{../Draft_Summer2018/MainFigures}
\def \ourTablePath {../../Tables/} 
\def\myFigWidth{2.0in}
\def\myFigWidthAlt{1.5in}

@@

\title[ICT \& medium-run TFP]{ICT and Future Productivity: Evidence and Theory of a GPT}

@@

\AtBeginSection[]
{
  \begin{frame}<beamer>
    \frametitle{Roadmap}
    \tableofcontents[currentsection]
  \end{frame}
}

@@

		\item Key prediction: BC fluctuations of a particular kind of investment (research \& development (R\&D) $\rightarrow$ adoption) lead total factor productivity (TFP).

@@

	Fernald et al. (2017): ``R\&D and adoption can't be the whole story''.

@@

		\item [$\rightarrow$] A suspect is investment in information and communication technologies (ICT).

@@

    \item Draw on the conclusions of the ICT literature to build a structural model to interpret the results.

@@

@@

	\item ICT and productivity 
		\begin{itemize}
		\item Jorgenson \& Stiroh (1999), Oliner \& Stichel (2000),  Brynjolffson \& Lorin (2000), Stiroh (2002) %Brynjolffson \& Yang (1999) %use stock market valuations of firms to identify the value of IT assets
		\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
\section{SVAR Analysis}
%%%%%%%%%%%%%%%%%%%%%%%%%

@@

	\begin{itemize}
	\item ICT value added is less than 5\% of GDP (BEA, April 2018).

@@

	\item Prediction of multisector models (GHK): sectoral productivity increase leads to sectoral output becoming cheaper.

@@

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{Results II}
	\label{results2}

@@

\hyperlink{largeVAR}{\beamerbutton{Results for a larger-scale VAR}}	
\end{frame}
%%%%%%%%%%%%%%%%%

@@

\item[$\rightarrow$] Alternative specification filters out news to recover an alternative ICT shock series.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Structural Model}
%%%%%%%%%%%%%%%%%%%%%%%%%

@@

	\begin{itemize}
	\item Belongs to the class of Greenwood, Hercowitz \& Krusell (GHK) models.

	(We use isomorphic formulation of Oulton (2007).)

@@

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{IRFs for a larger-scale VAR I (2 lags)}
	\label{largeVAR}

\begin{figure}[h!]
\begin{center}
\includegraphics[scale=0.25]{\ourFigPath Figures/fig_ICT_Shock_on_TFPUtil_empirical_fullEconomy}
%\caption{Setting $\gamma =0.1$}
\end{center}
\end{figure}

\hyperlink{results2}{\beamerreturnbutton{Return}}	
\end{frame}
%%%%%%%%%%%%%%%%%

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{IRFs for a larger-scale VAR II (2 lags)}

\begin{figure}[h!]
%\caption{Best Responses of $\sigma_1^2$} 
%\centering

\subfigure{\includegraphics[width=  \myFigWidthAlt]{\ourFigPath Figures/fig_ICT_Shock_on_Consumption_empirical_fullEconomy}} \hspace{.2in%
} 
\subfigure{\includegraphics[width=   \myFigWidthAlt]{\ourFigPath Figures/fig_ICT_Shock_on_GDP_empirical_fullEconomy}} \hspace{.2in%
} 
\subfigure{\includegraphics[width=   \myFigWidthAlt]{\ourFigPath Figures/fig_ICT_Shock_on_Hours_empirical_fullEconomy}} \hspace{.2in%
} 
\subfigure{\includegraphics[width=   \myFigWidthAlt]{\ourFigPath Figures/fig_ICT_Shock_on_ICTInvestment_empirical_fullEconomy}} \hspace{.2in%
} 
\subfigure{\includegraphics[width=   \myFigWidthAlt]{\ourFigPath Figures/fig_ICT_Shock_on_Investment_empirical_fullEconomy}} \hspace{.2in%
} 
\subfigure{\includegraphics[width=   \myFigWidthAlt]{\ourFigPath Figures/fig_ICT_Shock_on_RelativePriceICT_empirical_fullEconomy}} 
\end{figure}
